Rusty Variation

### 2018-06-15 doc/main.tex
Bumped release to v1.0.0
Inserted link to GitHub

\begin{document}
\title{Rusty Variation}
\subtitle{Deadlock-free Sessions with Failure in Rust}
\author{Wen Kokke}
\authornote{%
  Graduate student (8450698), supervised by Philip Wadler and Ian Stark.}
\affiliation{%
  LFCS, University of Edinburgh, 10 Crichton St,
  EH8 9AB, Edinburgh, United Kingdom}
\email{wen.kokke@ed.ac.uk}

@@

In this paper, we present Rusty Variation, a library for session-typed communication in Rust which allows users to specify and check the adherence to communication protocols, in addition to offering strong correctness guarantees, such as freedom from deadlocks and races.
We assume some familiarity with Rust. For an introduction to Rust, we refer the reader to \textit{The Rust Programming Language}.\footnote{\url{https://doc.rust-lang.org/nightly/book/}}

>>>>

\begin{document}
\title{Rusty Variation}
\subtitle{Deadlock-free Sessions with Failure in Rust}
\author{Wen Kokke}
\authornote{%
  Graduate student (9727050), supervised by Philip Wadler and Ian Stark.}
\affiliation{%
  LFCS, University of Edinburgh, 10 Crichton St,
  EH8 9AB, Edinburgh, United Kingdom}
\email{wen.kokke@ed.ac.uk}

@@

In this paper, we present Rusty Variation\footnote{\url{https://github.com/wenkokke/rusty-variation}}, a library for session-typed communication in Rust which allows users to specify and check the adherence to communication protocols, in addition to offering strong correctness guarantees, such as freedom from deadlocks and races.
We assume some familiarity with Rust. For an introduction to Rust, we refer the reader to \textit{The Rust Programming Language}.\footnote{\url{https://doc.rust-lang.org/nightly/book/}}
